---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# prioritizrshiny

The goal of prioritizrshiny is to ...

[![lifecycle](https://img.shields.io/badge/Lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis Build Status](https://img.shields.io/travis/prioritizr/prioritizrshiny/master.svg?label=Linux%20%26%20Mac%20OSX)](https://travis-ci.org/prioritizr/prioritizrshiny)

## Installation

The latest official version of the _prioritizrshiny R_ package can be installed using the following _R_ code.

```{r, eval = FALSE}
#Package is not on CRAN yet
#install.packages("prioritizrshiny", repos = "https://cran.rstudio.com/")
```

Alternatively, the latest development version can be installed using the following code. Please note that while developmental versions may contain additional features not present in the official version, they may also contain coding errors.

```{r, eval = FALSE}
if (!require(devtools))
  install.packages("devtools")
devtools::install_github("prioritizr/prioritizrshiny")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(prioritizrshiny)

# run the Shiny app
prshiny()

```
